Method to infer relatedness using low coverage ancient DNA

### 2021-12-23 paper_overleaf/main.tex
added supplementary info legends

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/contam0_inbred0_model_performance_allroc_asc0_plot.png}
    \caption{False positive and negative rates as a function of cutoff on log likelihood ratio. Dotted line represents $5\%$$}
    \label{fig3}
\end{figure}

@@

\section{Supplementary Information}
-binomial,betabinomial

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/binom.png}
    \caption{Beta binomial distribution is a better fit compared to Binomial for proportion of difference in windows}
    \label{figS1}
\end{figure}

@@

#Methods
$$\sum_{w} \sum_{I}\sum_\omega \log P(D_{w}|Z_w, H_w)k_{w\omega i}$$

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/contam0_inbred0_model_performance_allroc_asc0_plot.png}
    \caption{False positive and negative rates as a function of cutoff on log likelihood ratio. Dotted line represents $5\%$}
    \label{fig3}
\end{figure}

@@

\section{Supplementary Information}
Beta binomial distribution is a better fit compared to Binomial distribution for proportion of differences in windows.
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/binom.png}
    \caption{Comparison of fit with Betabinomial and Binomial distributions on (A) unrelated, (B) Parent-Child, (C) Identical pair of individuals.}
    \label{figS1}
\end{figure}

Results from KIn agree with results from READ, and provide some more information about siblings/parent-child, and $3^{rd}$ Degree relatedness. 
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/fil0_read_plot.png}
    \caption{Application of READ on Neandertal specimens from Chagyrskaya cave. Color of a square represents the relatedness, while the number denotes standard deviations away from the upper threshold (we show lower threshold for unrelated pairs since upper threshold is not available).}
    \label{figS2}
\end{figure}

Constraining variance of beta distributions in case of an identical pair, when identical relatedness hmm is applied, gives more accurate emission probabilities.
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_pair0_15_relid_emissions_bnds.png}
    \caption{Application of identical relatedness HMM on a pair of identical individuals with low coverage (0.2x), and ROH tracts. Top panel shows pairwise proportion of differences is close to expectation, but dips in some windows due to presence of ROH tracts. Bottom two panels show $P(Data|Z=2)$ without constraints and with constraints respectively.}
    \label{figS3}
\end{figure}

In figS4, the emissions improve in accuracy with constraints on variance of Beta distributions. figS5 shows why we see this improvement. With variance constraints, beta distributions corresponding to Z=1 and Z=2 do not overfit the data, and higher emission probabilities seen in (A) at $D_w/N_w$=0.05 disappear. All probability distributions are scaled by the same factor so they are visible with the data histogram.
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_pair0_15_relid_betaplot.png}
    \caption{Comparison of beta distributions estimated with the HMM (A) without and (B) with variance constraints.}
    \label{figS3}
\end{figure}

Restricting the emission probabilities at 1 for Y=1, in windows that have higher than $p_0$ difference improves the estimated Beta parameters. 
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_ind0_foreced_roh.png}
    \caption{Comparison of Beta distributions (A) without and (B) with modified emissions}
    \label{figS3}
\end{figure}

*Remember to use updated lcMLkin in the plot.
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/lcPlot.png}
    \caption{Comparison of IBD states estimated for Chagyrskaya specimens using (A) lcMLkin and (B) KIn.}
    \label{figS4}
\end{figure}

This figure shows that it is possible to differentiate between Avuncular and Grandparent-Grandchild pairs.
However, differentiating between Half-siblings may not be possible with our approach. 
*Add 1M windows result
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/degree2_10Mwin.png}
    \caption{Clustering of Avuncular, Half-siblings and Grandparent-Grandchild pairs using IBD estimation in simulations.}
    \label{figS5}
\end{figure}

-ROH high diff

@@

Methods
$$\sum_{w} \sum_{I}\sum_\omega \log P(D_{w}|Z_w, H_w)k_{w\omega i}$$
